---
title: "GraphST-R"
output: html_notebook
---


```{r}
library(SpatialExperiment)#library(Matrix) 
library(dplyr)#similar to pandas
library(torch)#similar to PyTorch in Python
library(pbapply)#R Equivalent of Python's tqdm
library(Matrix)#For sparse matrix operations
library(R6) #Load the R6 library
library(Dict)
library(transport)
library(otinference)
library(Seurat)# Load data and create a Seurat object, analogous to using scanpy
library(FNN) 
library(reticulate)
library(stats)
library(stats)
library(igraph)
library(leiden)
library(leidenAlg)


```

##Load your data in
```{r}
data_dir <- "data/GraphData"
spe <- SpatialExperiment::read10xVisium(samples = data_dir,
                                   type = "HDF5",
                                   data = "filtered")
```

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

